Mining the human microbiome for clinical insight

### 2018-12-20 chap_conclusion.tex
Move acknowledgments + make pared down versions of thesis

A turning point in my thesis came when I read Gene Glass's 1976 paper coining the term ``meta-analysis'' \cite{glass-1976}.
In it, Glass argues for the underappreciated importance of consolidating and synthesizing information into knowledge, prizing work that aims to find meaning and draw conclusions from disparate existing studies.
This was a turning point in my thesis for two reasons.
First, it was the moment I became truly proud of my work, especially the meta-analysis in Chapter 3: I realized that it was not just some sort of microbiome ``stamp collection'' endeavor that anyone with basic knowledge of computational tools could do, but was instead difficult and valuable work that I had uniquely contributed to.
After reading this piece, my perspective on my thesis work changed: before, I sometimes felt that the inherent limitations of computational work meant that projects like mine were not quite as valuable as theses which develop novel experimental methods or generate new data directly testing biological hypotheses.
Now, I recognize that they are also invaluable work on their own merit.
Second, reading Glass's words helped me recognize a uniting theme in all of my work: finding the ``knowledge in the information.''
I realized that in each project presented in this thesis, I had not just mined the data to find statistical associations, but rather to interpret associations and chase them all the way to their potential clinical or public health implications.
I hope that as we move forward in this exciting and vibrant field, microbiome researchers collectively become less satisfied with simply reporting new information, instead emphasizing and valuing efforts that synthesize existing knowledge and generate new insights that lead more directly to clinical impact.

>>>>

A turning point in my thesis came when I read Gene Glass's 1976 paper coining the term ``meta-analysis'' \cite{glass-1976}.
In it, Glass argues for the underappreciated importance of consolidating and synthesizing information into knowledge, prizing work that aims to find meaning and draw conclusions from disparate existing studies.
This was a turning point in my thesis for two reasons.
First, it was the moment I became truly proud of my work, especially the meta-analysis in Chapter 3: I realized that it was not just some sort of microbiome ``stamp collection'' endeavor that anyone with basic knowledge of computational tools could do, but was instead difficult and valuable work that I had uniquely contributed to.
After reading this piece, my perspective on my thesis work changed: before, I sometimes felt that the inherent limitations of computational work meant that projects like mine were not quite as valuable as theses which develop novel experimental methods or generate new data directly testing biological hypotheses.
Now, I recognize that they are also invaluable work on their own merit.
Second, reading Glass's words helped me recognize a uniting theme in all of my work: finding the ``knowledge in the information.''
I realized that in each project presented in this thesis, I had not just mined the data to find statistical associations, but rather to interpret the associations I found and chase them all the way to their potential clinical or public health implications.
I hope that as we move forward in this exciting and vibrant field, microbiome researchers collectively become less satisfied with simply reporting new information, instead emphasizing and valuing efforts that synthesize existing knowledge and generate new insights that lead more directly to clinical impact.

### 2018-12-20 cover.tex
Move acknowledgments + make pared down versions of thesis

\author{Claire Marie Noëlle Duvallet}

@@

\section*{Acknowledgments}

Mentors:
Rafa - will always be a friend of the lab
Jim
Deb
Ilana - for being the mentor I didn't know I needed

Thomas - being my first introduction to computational work with patience and enthusiasm, enabling me to find my passion here
Mariana - drive and ability to make impossible things actually happen was an inspiration, expanded the scope of what a PhD student could do
Scott - being a role model, mentor, collaborator, and now close friend. Hope you remain all four forever. Also for encouraging me to start doing diversity and REFS
Sean Gibbons - modeling pure interest in science for the sake of science, encouraging me and being patient when I thought it was all fake, modeling success and being a joy to work with

Peers:
Nathaniel
Diversity co-conspirators: Scott and Manu, Bevin, and now my GSC crew for revitalizing me in the work (Nas, Josue, Danielle, German, Halston, and Bianca)

Funding:
NDSEG
Siebel

Friends, family, and frisbee
Carolyn and Megan
Andee and Shelby
Janyne for keeping me adventuring
sMITe
Felix (for GTD, 20% rule, and inspiration to version control everything)
ET (for putting us to shame by having a job and real life)
Parents (for supporting me, recognizing my passions better than I do, and listening to me talk about poop over many dinners)

>>>>

\author{Claire Marie No{\"e}lle Duvallet}

@@
